Smelt Cage Histopathology

### 2023-07-11 histopathology.Rmd
a few more graphs and some test of histopathology stats

ggplot(goodgills, aes(x = treatment, y = gill, fill = season)) +
  geom_boxplot()
```

@@

>>>>

ggplot(goodgills, aes(x = treatment, y = gill, fill = season)) +
  geom_boxplot()

@@

Now compare rio vista in fall versus suisun marsh in fall

fallgills = mutate(gills, Fgill = factor(gill, ordered = T)) %>%
  filter(season == "Fall")
c1f = clm(Fgill ~ treatment, data = fallgills)
summary(c1f)

convergence(c1f)
autoplot.clm(c1f)
#beautiful!

#can I do a post hoc?
library(emmeans)
emmeans(c1f, pairwise ~ treatment)
